Dataset-level report

### 2019-11-08 analysis/reports/dat_report_template.Rmd
fix templating

---
title: "Dataset-level report"
output: 
  github_document:
    html_preview: false
params:
  dataset_name: ["mcdb"]
---

@@

>>>>

---
title: "Dataset-level report"
output: 
  github_document
params:
  dataset_name: ["mcdb"]
---

@@

## Number of samples achieved

```{r number of samples}

site_samples <- all_di %>%
  select(sim, source, site, singletons) %>%
  group_by(source, site, singletons) %>%
  summarize(nsamples = length(unique(sim))) %>%
  ungroup() %>%
  filter(source == "sampled") %>%
  left_join(select(sv, -source, -sim), by = c("site", "singletons"))
```

#### The maximum number of samples achieved is `r max(site_samples$nsamples)`.

```{r plot nb samples}
samples_hist <- ggplot(data = site_samples, aes(x = nsamples)) +
  geom_histogram(binwidth = 10) +
  theme_bw() +
  facet_wrap(vars(singletons), nrow = 1) +
  ggtitle("Number of samples achieved")

samples_hist

sv_samples_plot <- ggplot(data = site_samples, aes(x = s0, y = n0, color = nsamples)) +
  geom_point(alpha = .5) +
  theme_bw() +
  facet_wrap(vars(singletons), nrow = 1) +
  scale_color_viridis_c(option = "magma", end = .75) +
  ggtitle("Number of samples achieved by state variables")
sv_samples_plot

```
